Supplemental Material for \\ Helixer: Cross-species Gene Annotation of Large Eucaryotic Genomes Using Deep Learning

### 2020-04-24 paper/supplements.tex
removed comments
minor, images commented out again

\newpage
\section{Model Evaluation by Species}
The following tables and plots show the prediction performance of Hexlixer for each species we worked with. An F1 score of zero can indicate that the reference did not include that class. The plots display the Subgenic F1 as well as the difference to AUGUSTUS with respect to the phylogenetic placement by the NCBI taxonomy database \citep{federhen2012ncbi}.

@@

\renewcommand\refname{Supplemental Reference}
\bibliographystyle{natbib}
\bibliography{literature}

>>>>

\newpage
\section{Model Evaluation by Species}
The following tables and plots show the prediction performance of Helixer for each species we worked with. The tables show a breakdown by basepair level accuracy, F1 score for each individual class and our two overall metrics, the Subgenic F1 and Genic F1. An F1 score of zero can indicate that the reference did not include that class.

The plots display the raw Subgenic F1 score as well as the difference to AUGUSTUS in Subgenic F1 with respect to the phylogenetic placement by the NCBI taxonomy database \citep{federhen2012ncbi}.

@@

\renewcommand\refname{Supplemental References}
\bibliographystyle{natbib}
\bibliography{literature}
